Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich A lightweight design to convolution-based deep learning CSI feedback

@@

>>>>

\cite{li2024lightweight}Proposes GCRNet, a Ghost module-based architecture that reduces feature redundancy in CSI feedback by generating secondary features from primary maps. Achieves 22.15\% lower complexity than \cite{clnet} while maintaining comparable accuracy, addressing efficiency decay in convolution-based methods like \cite{csinet}.

@@

	\bibitem{li2024lightweight}
	X. Li, Y. Wang, and Z. Zhang, ``A lightweight design to convolution-based deep learning CSI feedback,'' \textit{IEEE Wireless Commun. Lett.}, 2024.
